Delayed effects of [responses to?] climate lead to demographic divergence in a fragmented Amazonian landscape

### 2021-05-07 doc/paper.Rmd
change figure size and font size to be more consistent

```{r normals, fig.cap=normals_cap}
normals_plot
```

@@

```{r eda, fig.cap=eda_cap}
eda_plot
```

@@

```{r size-plot, fig.cap=size_cap, fig.height=6, fig.width=5}
size_plot
```

@@

```{r surv-spei, fig.cap=s_spei_cap, fig.height=5, fig.width=7}
s_spei_plot
```

@@

```{r surv-diff, fig.cap=s_spei_diff_cap, fig.height=2.5, fig.width=7}
s_spei_diff_plot
```

@@

```{r growth-spei, fig.cap=g_spei_cap, fig.height=5, fig.width=7}
g_spei_plot
```

@@

```{r growth-diff, fig.cap=g_spei_diff_cap, fig.height=2.5, fig.width=7}
g_spei_diff_plot
```

@@

```{r flwr-spei, fig.cap=f_spei_cap, fig.height=5, fig.width=7}
f_spei_plot
```

@@

```{r flwr-diff, fig.cap=f_spei_diff_cap, fig.height=2.5, fig.width=7}
f_spei_diff_plot
```

>>>>

```{r normals, fig.cap=normals_cap}
normals_plot & theme(text = element_text(size = 10))
```

@@

```{r eda, fig.cap=eda_cap, fig.width=7, fig.height=7}
eda_plot & theme(text = element_text(size = 10))
```

@@

```{r size-plot, fig.cap=size_cap, fig.width=7, fig.height=7}
size_plot & theme(text = element_text(size = 10))
```

@@

```{r surv-spei, fig.cap=s_spei_cap, fig.height=5, fig.width=7}
s_spei_plot & theme(text = element_text(size = 10))
```

@@

```{r surv-diff, fig.cap=s_spei_diff_cap, fig.height=2.5, fig.width=7}
s_spei_diff_plot  & theme(text = element_text(size = 10))
```

@@

```{r growth-spei, fig.cap=g_spei_cap, fig.height=5, fig.width=7}
g_spei_plot & theme(text = element_text(size = 10))
```

@@

```{r growth-diff, fig.cap=g_spei_diff_cap, fig.height=2.5, fig.width=7}
g_spei_diff_plot & theme(text = element_text(size = 10))
```

@@

```{r flwr-spei, fig.cap=f_spei_cap, fig.height=5, fig.width=7}
f_spei_plot & theme(text = element_text(size = 10))
```

@@

```{r flwr-diff, fig.cap=f_spei_diff_cap, fig.height=2.5, fig.width=7}
f_spei_diff_plot & theme(text = element_text(size = 10))
```
